A patch-based framework for new ITK functionality: Joint fusion, denoising, and non-local super-resolution

### 2017-03-15 Document/LaTeX/ArticleExample.tex
ENH:  UPdate text.

% At minimum, give your name and an email address.  You can include a
% snail-mail address if you like.
\author{Nick Tustison$^{1}$ Brian Avants$^{2}$, Long Xie$^{3}$, Paul Yushkevich$^{3}$, and Jose Vicente Manj\'on$^{4}$}
\authoraddress{$^{1}$University of Virginia, Charlottesville, VA\\
               $^{2}$Biogen, Cambridge, MA\\
               $^{3}$University of Pennsylviania, Philadelphia, PA\\
               $^{4}$ITACA institute, Universidad Polit\'ecnica de Valencia, Valencia, Spain
               }

@@

% The abstract should be a paragraph or two long, and describe the
% scope of the document.
\begin{abstract}
\noindent
In an earlier Insight Journal article, we introduced an ITK implementation of the
adaptive patch-based image denoising algorithm described in \cite{Manjon:2010aa}.
We follow-up up that offering with a generalized non-local, patch-based ITK class
framework and a refactored denoising class.  In addition, we provide two additional
ITK implementations of related, well-known algorithms.  The first is a non-local
super resolution method described in \cite{Manjon:2010ab,Manjon:2010ac}.  The second is
the multivariate
joint label fusion algorithm of \cite{Wang:2013ab,Wang:2013aa}.  Accompanying these ITK classes are
documented programming interfaces which use our previously introduced unique
command line interface routines.  Several 2-D examples on brain imaging data are
provided to qualitatively demonstrate performance.
\end{abstract}

@@

Image filtering techniques are usually applied to increase the quality of MR images.
Most of these techniques assume an equal noise distribution across the image. When this
assumption is not met, the resulting filtering becomes suboptimal. This is the case of MR
images with spatially varying noise levels, such as those obtained by parallel imaging
(sensitivity-encoded), intensity inhomogeneity-corrected images or surface coil based
acquisitions. In this work, we have adapted a recently proposed filter so-called
Non-Local Means (NL-means) to deal with MR images with spatially varying noise levels
(for both Gaussian and Rician distributed noise). With this new method, information
regarding the local image noise level is used to adjust the amount of denoising strength
of the filter. Such information is automatically obtained from the images by using the
local noise estimation method described in \cite{Manjon:2010aa}.

This method has been validated and compared with the standard NL-means filter on simulated
and real MR imaging data. This noise-adaptive NL-means method was demonstrated to outperform
the standard NL-means based filter when spatially varying noise is present in the images.
Although source code is available from Prof. Manj\'on Herrera's website
(http://personales.upv.es/jmanjon/denoising/arnlm.html).  This particular algorithm is
currently not available in the Insight Toolkit which provides good performance with minimal
parameter tuning. In this Insight Journal submission, we provide a brief overview of the ITK
implementation and provide a couple examples.

>>>>

% At minimum, give your name and an email address.  You can include a
% snail-mail address if you like.
\author{Nick Tustison$^{1}$ Brian Avants$^{2}$, Hongzhi Wang$^{3}$, Long Xie$^{4}$, Paul Yushkevich$^{4}$, and Jose Vicente Manj\'on$^{5}$}
\authoraddress{$^{1}$University of Virginia, Charlottesville, VA\\
               $^{2}$Biogen, Cambridge, MA\\
               $^{3}$IBM, San Jose, CA\\
               $^{4}$University of Pennsylviania, Philadelphia, PA\\
               $^{5}$ITACA institute, Universidad Polit\'ecnica de Valencia, Valencia, Spain
               }

@@

% The abstract should be a paragraph or two long, and describe the
% scope of the document.
\begin{abstract}
\noindent
In an earlier Insight Journal article, we introduced an ITK implementation of the
adaptive patch-based image denoising algorithm described in \cite{Manjon:2010aa}.
We follow-up up that offering with a generalized non-local, patch-based ITK class
framework and a refactored denoising class.  In addition, we provide two
ITK implementations of related, well-known algorithms.  The first is a non-local
super resolution method described in \cite{Manjon:2010ab,Manjon:2010ac}.  The second is
the multivariate
joint label fusion algorithm of \cite{Wang:2013ab,Wang:2013aa} with additional extensions,
denoted as ``joint intensity fusion'', which will be described in a forthcoming manuscript.
Accompanying these ITK classes are
documented programming interfaces which use our previously introduced unique
command line interface routines.  Several 2-D examples on brain imaging data are
provided to qualitatively demonstrate performance.
\end{abstract}

@@

Since the non-local (NL) means algorithm introduced in several early papers \cite{Buades},
the resulting family of research techniques has grown to significant prominence within the
medical imaging community.  In addition to continued research output, patch-based techniques
have been the subject of workshops (Patch-MI 2015 and PMI'16, both MICCAI-sponsored
workshops).   Given the interest and potential applications, this submission is a potential
``conversation starter'' for the development of an ITK software framework
